Realizability-Preserving DG-IMEX Method for the Two-Moment Model of Fermion Transport \tnoteref{support}

### 2018-04-02 Documents/M1/realizableFermionicM1/sections/appendix.tex
Added the details of SSPRK2 and SSPRK3.
Adjustments to the text on IMEX AP2+

We here give another second-order accurate, sitivity-preserving IMEX scheme of type $A$, named IMEX PA2+, which has a lager $c_{sch}$ than IMEX PA2.
It was chosen from $10^{6}$ coefficient groups that satisfy both the second-order accuracy requirement and the positivity-preserving requirement.
IMEX PA2+ is the one has the largest ($c_{sch} = 0.895041066934$). 
Its non-zero components of $\tilde{A}$ and $A$ are given by
\begin{align}
  \tilde{a}_{21} &= 0.909090909090909, \nonumber \\
  \tilde{a}_{31} &= 0.450000000000000, \quad \tilde{a}_{32} = 0.550000000000000, \nonumber \\
  a_{11} &= 0.521932391842510, \nonumber \\
  a_{21} &= 0.479820781424967, \quad a_{22} = 0.002234534340252, \nonumber \\
  a_{31} &= 0.499900000000000, \quad a_{32} = 0.001100000000000, \quad a_{33} = 0.499000000000000. \nonumber
\end{align}
The coefficient in the correction step is $\alpha = 0.260444263529413$.  
This scheme is also a GSA scheme: $\tilde{w}_{i}=\tilde{a}_{3i}$ and $w_{i}=a_{3i}$ for $i\le3$.

@@

>>>>

We have found another second-order accurate, positivity-preserving IMEX scheme of type $A$, which we refer to as IMEX PA2+.  
This scheme allows for has a larger $c_{sch}$ than IMEX PA2 (i.e., a larger time step for positivity).  
The scheme chosen by random sampling of the parameter space, and was the scheme with the largest $c_{sch}$ that satisfied both the order conditions for second order accuracy and possessed the positivity-preserving property.  
For IMEX PA2+, ($c_{sch} = 0.895041066934$). 
The non-zero components of $\tilde{A}$ and $A$ are given by
\begin{align}
  \tilde{a}_{21} &= 0.909090909090909, \nonumber \\
  \tilde{a}_{31} &= 0.450000000000000, \quad \tilde{a}_{32} = 0.550000000000000, \nonumber \\
  a_{11} &= 0.521932391842510, \nonumber \\
  a_{21} &= 0.479820781424967, \quad a_{22} = 0.002234534340252, \nonumber \\
  a_{31} &= 0.499900000000000, \quad a_{32} = 0.001100000000000, \quad a_{33} = 0.499000000000000. \nonumber
\end{align}
The coefficient in the correction step is $\alpha = 0.260444263529413$.  
This scheme is also GSA; $\tilde{w}_{i}=\tilde{a}_{3i}$ and $w_{i}=a_{3i}$ for $i\le3$.

@@

A second-order accurate, strong-stability-preserving explicit Runge-Kutta scheme, referred as SSPRK2, has the following non-zero components:
\begin{align}
  \tilde{a}_{21} &= 1, \nonumber \\
  \tilde{w}_{1} &= 1/2, \quad \tilde{w}_{2} = 1/2. \nonumber 
\end{align}
A third-order accurate, strong-stability-preserving explicit Runge-Kutta scheme, was referred as SSPRK3.
It has the following non-zero components:
\begin{align}
  \tilde{a}_{21} &= 1, \nonumber \\
  \tilde{a}_{31} &= 1/4, \quad \tilde{a}_{32} = 1/4, \nonumber \\
  \tilde{w}_{1} &= 1/6, \quad \tilde{w}_{2} = 1/6, \quad \tilde{w}_{3} =2/3 \nonumber
\end{align}
